---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
require(svglite)
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    dev = "svglite",
    fig.path = "man/figures/README-",
    fig.showtext = TRUE,
    fig.width = 7,
    fig.height = 4,
    out.width = "100%"
)
```

# Emplot

<!-- badges: start -->
<!-- badges: end -->

A clean theme for `ggplot2` with matching `geom` defaults.

## Installation

Install from [GitHub](https://github.com/) using the [devtools](https://cran.r-project.org/web/packages/devtools) package:

```{r, eval = FALSE}
devtools::install_github("dbarrows/emplot")
```

Possible CRAN version in the future.

## Examples

```{r libraries}
library(ggplot2)
library(emplot)
```
```{r scatter}
ggplot(mpg, aes(displ, hwy, color = class)) +
    geom_point()
```

```{r histogram}
ggplot(mpg, aes(displ)) +
    geom_histogram(bins = 30)
```

## Options

The grid can be forced on/off with the `grid` option:

```{r grid_off}
library(tidyverse)
library(gapminder)
as_tibble(gapminder) %>%
    mutate(cc = I(country_colors[match(country, names(country_colors))])) %>%
    filter(continent %in% c("Africa", "Europe") & year == 2007) %>%
    ggplot(aes(log(gdpPercap), lifeExp)) +
        geom_point(aes(colour = cc, size = sqrt(pop/pi)/1500)) +
        theme_emplot(grid = FALSE) +
        theme(legend.position = "none")
```

The font can be changed to a serif with the `serif` option (for the [Tufte](https://www.edwardtufte.com/tufte/) look):

```{r serif_on}
ggplot(iris, aes(Petal.Length)) +
    geom_histogram(bins = 30) +
    scale_y_continuous(breaks = seq(5, 25, by = 5)) +
    geom_hline(yintercept = seq(5, 25, by = 5), col = "white") +
    theme_emplot(grid = FALSE, serif = TRUE)
```

```{r tufte_line}
library(tidyverse)
mpg %>%
    mutate(cyl = as.factor(cyl)) %>%
    ggplot(aes(displ, hwy, color = cyl)) +
        geom_point() +
        geom_smooth(method = lm, se = FALSE) +
        theme_emplot(grid = FALSE, serif = TRUE) +
        scale_color_grey(end = 0.75)
```

You can also use `theme_emtufte` to reproduce the Tufte look out-of-the-box:

```{r tufte_scatter}
mtcars %>%
    ggplot(aes(disp, hp)) +
        geom_point() +
        theme_emtufte()
```