---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
require(svglite)
set.seed(42)
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    dev = "svglite",
    fig.path = "man/figures/README-",
    fig.showtext = TRUE,
    fig.width = 7,
    fig.height = 4,
    out.width = "100%",
    message = FALSE
)
```

# wplot

<!-- badges: start -->
[![R build status](https://github.com/dbarrows/wplot/workflows/R-CMD-check/badge.svg)](https://github.com/dbarrows/wplot/actions)
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
<!-- badges: end -->

A clean theme for `ggplot2` with matching `geom` defaults.

## Installation

Install from [GitHub](https://github.com/) using the [devtools](https://cran.r-project.org/web/packages/devtools) package:

```{r, eval = FALSE}
devtools::install_github("dbarrows/wplot")
```

Possible CRAN version in the future.

## Examples

### Light Theme

```{r, include = FALSE}
devtools::load_all()
library(ggplot2)
library(magrittr)
library(tibble)
```
```{r, eval = FALSE}
library(wplot)
library(ggplot2)
library(magrittr)
library(tibble)
```

```{r scatter}
ggplot(mpg, aes(displ, hwy, colour = class)) +
    geom_point() +
    theme_wl()
```

```{r histogram}
ggplot(mpg, aes(displ)) +
    geom_histogram(bins = 30) +
    theme_wl()
```

### Options

The grid can be turned on/off with the `grid` option, and the font can be a made `serif`:

```{r grid_off, message  = FALSE}
library(tidyverse)
library(gapminder)

gapminder %>%
    mutate(cc = I(country_colors[match(country, names(country_colors))])) %>%
    filter(continent %in% c("Africa", "Europe") & year == 2007) %>%
    ggplot(aes(log(gdpPercap), lifeExp)) +
        geom_point(aes(colour = cc, size = sqrt(pop/pi)/1500)) +
        theme_wl(grid = FALSE, serif = TRUE) +
        theme(legend.position = "none")
```

### Dark theme

```{r scatter-dark}
library(colorblindr)

ggplot(mpg, aes(displ, hwy, colour = class)) +
    geom_point() +
    theme_wd() +
    scale_colour_OkabeIto() +
    theme(plot.margin = margin(1, 1, 1, 1, "cm"))
```

```{r histogram-dark}
ggplot(mpg, aes(hwy)) +
    geom_histogram(bins = 30) +
    theme_wd() +
    theme(plot.margin = margin(1, 1, 1, 1, "cm"))
```

```{r math-dark}
tibble(x = seq(0, 100, length.out = 50),
       y = sqrt(x) + rnorm(length(x))) %>%
    ggplot(aes(x, y)) +
        geom_point() + 
        geom_smooth() +
        theme_wd() +
        theme(plot.margin = margin(1, 1, 1, 1, "cm"))
```

### Classic theme

For a slightly larger serif font, smaller points, and no grid.

```{r classic_scatter}
mpg %>%
    ggplot(aes(displ, cty)) +
    geom_point() +
    geom_smooth() +
    theme_wc()
```

### Tufte theme

You can get the [Tufte](https://www.edwardtufte.com/tufte/) look:

```{r tufte_scatter}
library(MASS)

Boston %>%
    ggplot(aes(ptratio, tax)) +
        geom_point() +
        geom_rug() +
        theme_wt()
```

```{r tufte_hist}
h <- Boston %>%
    pull(tax) %>%
    hist(plot = FALSE)
df <- h %>%
    with(tibble(tax = mids, count = counts))
ybreaks <- seq(20, max(df$count), by = 20)
df %>%
    ggplot(aes(tax, count)) +
        geom_col(orientation = "x", width = diff(h$breaks[1:2])/2) +
        scale_y_continuous(breaks = ybreaks) +
        theme_wt() +
        geom_hline(size = 0.75,
                   yintercept = ybreaks,
                   col = theme_wt()$plot.background$fill)
```
